---
title: "W_UP_01"
author: "Stephanie Bolanos"
date: "Summer 2022"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
Position is categorical variable. Push-ups is a numerical variable. I will do an analysis that explains push-ups based on position.


# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(pushups~position,data=mydata)
```

There are push-ups on the y-axis of the box plot, than there are on the x-axis. On the box plot there is a large segment on each whisker plot. The average push-ups for the positions appears to be different. The skill position appears to do more push-ups based off of the y-axis(push-ups)

### Numerical Descriptive Results
COME BACK

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results
```{r}
t.test(pushups~position,data=mydata)
```
P-value is 9.421e-06  df= 27.079  T=-5.4341
The alternative hypothesis is shown which states "true difference in means between group LINE and group SKILL is not equal to 0." The sample estimates are: mean in group LINE is 17.2500; mean in group SKILL 49.72. If the null hypothesis is true, the p-value is the probability of getting the results. LINE vs SKILL. It is very rare. The p-value is small we would reject the null hypothesis. If it's greater than .05, you failed to reject the null hypothesis. The SKILL group would be able to do more push ups.


<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

Based on the original question being who could do more push ups Line or Skill players under a specific amount of time given. Using a box plot and table it provided percentages and values comparing the push ups completed in a specific amount of time between the line and skill players. Basing our answer on the numerical descriptive results and the inferential results, it shows that Skill position players were able to do more push ups than Line position players could. The median and average was higher for Skill players. Concluding that Skill players completed more push ups than the line players in a timed matter.

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

